Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
recovery time comments

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

      r_times <-

>>>>

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'recovery_times'
  return(df)
}

@@

      r_times <- get_recovery()
